\newpage
Vision Statement 
1.     Reasons for wishing to pursue PhD studies in Hong Kong (max. 2000 characters)*
1)      ST background, interested in Social topics/questions, would like to further study.
2)      From 2008, stayed in HK more than 9 yrs, love HK. International version, culture and science. 
3)      Good place to study, blabla. Currently work in HK, so as to apply part time degree
2.     Long-term career plan, aims and interests for future development after graduation (max. 2000 characters)
1)      10+ yrs work experience, some kind of financial freedom. Aims to live for personal interest instead of money.
2)      Put effort on humanities or social sciences, relates to ST development, or by using ST logical method
3)      Form my own knowledge/cognitive system, present to the world someday….. e.g. write a book, design a course, arrange an exhibition…
3.     Contribution that you would like to make to the development of research in Hong Kong and to society (max. 2000 characters)*
1)       
4.     Other remarks in relation to the application for Hong Kong PhD Fellowship (max. 2000 characters)*
1)       

3.      Contribution that you would like to make to the development of research in Hong Kong and to society (max. 2000 characters)*
1)      Current works in ST industry, with research background, good understanding on HK technology and environment.  Good for research.
2)      Working experience in FMCG, IOT, management, aerospace, both China and HK,  have deep experience on social behavior, attitude, psychology. 
3)      Proposed research will contribute to the human being future……….. hahahaha


with multidisciplinary study background in the field of XXX, the research work are more likely conducted from a wider academic perspective with novel ideas and approaches. 

Participations in XXXX  project, extensive experience and personal network in relative high-tech projects. well trained with time management,experiment design, academic reading and writing,and other relative important qualities for being a phd.  

Working experiences in HKUST and PolyU, clear understanding of each step for the phd program. 